For the POS tagging, we used the word\_tokenize() function from the nltk library. The table below shows the results of POS tagging 5 random reviews.

\setlength{\tabcolsep}{18pt}
\renewcommand{\arraystretch}{1.75}
    \begin{longtable}{|| p{3cm} | p{3cm} ||} 
        \hline 
         \textbf{Review/Text} & \textbf{Parts of Speech} \\ [0.5ex] 
         \hline\hline
         The bubble tea was excellent! The service however, was not. I found it pushy, rushed, abrasive, and incredibly rude. Their way of dealing with English speaking customers is to bark at them until they leave with their order. You certainly won't be receiving any of my money ever again. & [('The', 'DT'), ('bubble', 'JJ'), ('tea', 'NN'), ('was', 'VBD'), ('excellent', 'JJ'), ('!', '.'), ('The', 'DT'), ('service', 'NN'), ('however', 'RB'), (',', ','), ('was', 'VBD'), ('not', 'RB'), ('.', '.'), ('I', 'PRP'), ('found', 'VBD'), ('it', 'PRP'), ('pushy', 'VBZ'), (',', ','), ('rushed', 'VBD'), (',', ','), ('abrasive', 'JJ'), (',', ','), ('and', 'CC'), ('incredibly', 'RB'), ('rude', 'VB'), ('.', '.'), ('Their', 'PRP\$'), ('way', 'NN'), ('of', 'IN'), ('dealing', 'VBG'), ('with', 'IN'), ('English', 'NNP'), ('speaking', 'VBG'), ('customers', 'NNS'), ('is', 'VBZ'), ('to', 'TO'), ('bark', 'VB'), ('at', 'IN'), ('them', 'PRP'), ('until', 'IN'), ('they', 'PRP'), ('leave', 'VBP'), ('with', 'IN'), ('their', 'PRP\$'), ('order', 'NN'), ('.', '.'), ('You', 'PRP'), ('certainly', 'RB'), ('wo', 'MD'), ("n't", 'RB'), ('be', 'VB'), ('receiving', 'VBG'), ('any', 'DT'), ('of', 'IN'), ('my', 'PRP\$'), ('money', 'NN'), ('ever', 'RB'), ('again', 'RB'), ('.', '.')] \\ 
         \hline
         I love the sketch comedy nights! Food is not so great. Drinks are average prices. Good venue. & [('I', 'PRP'), ('love', 'VBP'), ('the', 'DT'), ('sketch', 'NN'), ('comedy', 'NN'), ('nights', 'NNS'), ('!', '.'), ('Food', 'NNP'), ('is', 'VBZ'), ('not', 'RB'), ('so', 'RB'), ('great', 'JJ'), ('.', '.'), ('Drinks', 'NNS'), ('are', 'VBP'), ('average', 'JJ'), ('prices', 'NNS'), ('.', '.'), ('Good', 'JJ'), ('venue', 'NN'), ('.', '.')] \\
         \hline
         This place is inside Baiz Supermarket. If you are in mood of middle eastern food, this is the place. They have the most popular dishes. I highly recommend this place! & [('This', 'DT'), ('place', 'NN'), ('is', 'VBZ'), ('inside', 'JJ'), ('Baiz', 'NNP'), ('Supermarket', 'NNP'), ('.', '.'), ('If', 'IN'), ('you', 'PRP'), ('are', 'VBP'), ('in', 'IN'), ('mood', 'NN'), ('of', 'IN'), ('middle', 'JJ'), ('eastern', 'JJ'), ('food', 'NN'), (',', ','), ('this', 'DT'), ('is', 'VBZ'), ('the', 'DT'), ('place', 'NN'), ('.', '.'), ('They', 'PRP'), ('have', 'VBP'), ('the', 'DT'), ('most', 'RBS'), ('popular', 'JJ'), ('dishes', 'NNS'), ('.', '.'), ('I', 'PRP'), ('highly', 'RB'), ('recommend', 'VBP'), ('this', 'DT'), ('place', 'NN'), ('!', '.')] \\
         \hline
         I used to love Jukebox but after today's meal, all I can say is "it was nice while it lasted". That was the dryest, most flavorless burger I've ever had. The cook didn't even bother getting the patty all on the bun, but just slapped everything together in a sloppy, careless mess. The fries were way overcooked (it used to come with curly but those are now an extra \$\$). The bun was plain, untoasted and there was no tomato (there was supposed to be). \$18 for overpriced cardboard. & [('I', 'PRP'), ('used', 'VBD'), ('to', 'TO'), ('love', 'VB'), ('Jukebox', 'NNP'), ('but', 'CC'), ('after', 'IN'), ('today', 'NN'), ("'s", 'POS'), ('meal', 'NN'), (',', ','), ('all', 'DT'), ('I', 'PRP'), ('can', 'MD'), ('say', 'VB'), ('is', 'VBZ'), ('``', '``'), ('it', 'PRP'), ('was', 'VBD'), ('nice', 'RB'), ('while', 'IN'), ('it', 'PRP'), ('lasted', 'VBD'), ("''", "''"), ('.', '.'), ('That', 'DT'), ('was', 'VBD'), ('the', 'DT'), ('dryest', 'JJS'), (',', ','), ('most', 'JJS'), ('flavorless', 'JJ'), ('burger', 'NN'), ('I', 'PRP'), ("'ve", 'VBP'), ('ever', 'RB'), ('had', 'VBN'), ('.', '.'), ('The', 'DT'), ('cook', 'NN'), ('did', 'VBD'), ("n't", 'RB'), ('even', 'RB'), ('bother', 'VB'), ('getting', 'VBG'), ('the', 'DT'), ('patty', 'NN'), ('all', 'DT'), ('on', 'IN'), ('the', 'DT'), ('bun', 'NN'), (',', ','), ('but', 'CC'), ('just', 'RB'), ('slapped', 'VBD'), ('everything', 'NN'), ('together', 'RB'), ('in', 'IN'), ('a', 'DT'), ('sloppy', 'JJ'), (',', ','), ('careless', 'JJ'), ('mess', 'NN'), ('.', '.'), ('The', 'DT'), ('fries', 'NNS'), ('were', 'VBD'), ('way', 'NN'), ('overcooked', 'VBN'), ('(', '('), ('it', 'PRP'), ('used', 'VBD'), ('to', 'TO'), ('come', 'VB'), ('with', 'IN'), ('curly', 'JJ'), ('but', 'CC'), ('those', 'DT'), ('are', 'VBP'), ('now', 'RB'), ('an', 'DT'), ('extra', 'JJ'), ('\$', '\$'), ('\$', '\$'), (')', ')'), ('.', '.'), ('The', 'DT'), ('bun', 'NN'), ('was', 'VBD'), ('plain', 'RB'), (',', ','), ('untoasted', 'JJ'), ('and', 'CC'), ('there', 'EX'), ('was', 'VBD'), ('no', 'DT'), ('tomato', 'NN'), ('(', '('), ('there', 'EX'), ('was', 'VBD'), ('supposed', 'VBN'), ('to', 'TO'), ('be', 'VB'), (')', ')'), ('.', '.'), ('\$', '\$'), ('18', 'CD'), ('for', 'IN'), ('overpriced', 'VBN'), ('cardboard', 'NN'), ('.', '.')] \\
         \hline
         Scheduled manicure and pedicure one day. Came in, was seated and was told to wait. Waited for over 30 minutes, went back to the front desk, they said they forgot about me. I was nice about it, I guess that happenes (not at the good places, but still happens). At the end wasn't even offered a discount... pretty shitty move. & [('Scheduled', 'VBN'), ('manicure', 'NN'), ('and', 'CC'), ('pedicure', 'NN'), ('one', 'CD'), ('day', 'NN'), ('.', '.'), ('Came', 'NN'), ('in', 'IN'), (',', ','), ('was', 'VBD'), ('seated', 'VBN'), ('and', 'CC'), ('was', 'VBD'), ('told', 'VBN'), ('to', 'TO'), ('wait', 'VB'), ('.', '.'), ('Waited', 'VBN'), ('for', 'IN'), ('over', 'IN'), ('30', 'CD'), ('minutes', 'NNS'), (',', ','), ('went', 'VBD'), ('back', 'RB'), ('to', 'TO'), ('the', 'DT'), ('front', 'NN'), ('desk', 'NN'), (',', ','), ('they', 'PRP'), ('said', 'VBD'), ('they', 'PRP'), ('forgot', 'VBD'), ('about', 'IN'), ('me', 'PRP'), ('.', '.'), ('I', 'PRP'), ('was', 'VBD'), ('nice', 'JJ'), ('about', 'IN'), ('it', 'PRP'), (',', ','), ('I', 'PRP'), ('guess', 'VBP'), ('that', 'IN'), ('happenes', 'NNS'), ('(', '('), ('not', 'RB'), ('at', 'IN'), ('the', 'DT'), ('good', 'JJ'), ('places', 'NNS'), (',', ','), ('but', 'CC'), ('still', 'RB'), ('happens', 'VBZ'), (')', ')'), ('.', '.'), ('At', 'IN'), ('the', 'DT'), ('end', 'NN'), ('was', 'VBD'), ("n't", 'RB'), ('even', 'RB'), ('offered', 'VBN'), ('a', 'DT'), ('discount', 'NN'), ('...', ':'), ('pretty', 'RB'), ('shitty', 'JJ'), ('move', 'NN'), ('.', '.')] \\  
         \hline
    \end{longtable}

    

