For our analysis of the writing style, we picked some random sentences as a sample to compare it with articles in the well known newspaper “The Strait Times”, whereby we used the food section as a control sample. The list below shows our observations:

\begin{itemize}
    \item The last sentence does not have a final punctuation.
    \item The review lacks proper punctuation in the sentences.
    \item There is usage of words that are not in the English dictionary.
    \item There is use of slang. 
    \item The first words of the sentences in the review are not capitalized.
    \item The last sentence does not have a final punctuation.
    \item News articles are usually written in third person point of view, however the reviews from yelp are written in first person point of view.
    \item The first words of the sentences in the review are not capitalized.
    \item The last sentence does not have a final punctuation.
    \item News articles are usually written in third person point of view, however the reviews from yelp are written in first person point of view.
    \item The review contains onomatopoeia.
    \item The review uses all capitalised characters to create emphasis.
    \item News articles usually do not contain punctuation like ‘...’ that suggests pause.
    \item Words like ‘gal’ that is used to denote a girl is considered informal which is used in the review but not a news article.
    \item News articles usually use subject-verb-object construction for the sentences.
    \item The review contains many exclamation marks for one sentence although it is not necessary (known as “exclamation-point inflation” in digital communication).
    \item Some of the first words in sentences like ‘the’ are not capitalized.
    \item Personal pronouns like ‘i’ aren't capitalized.
    \item There are misspelled words, such as ‘espically’.
    \item There are missing punctuation in the reviews.
    \item The review is not relevant to the business.
    \item The review is not in full proper sentences.
    \item The review contains smileys (~2 \% of all reviews contain smileys).
\end{itemize}
